Fourmile Calibrations

### 2022-12-06 calibration_output.Rmd
added kge by water year

---
title: "Fourmile Calibrations"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

library(tidyverse)
library(plotly)

@@

write.csv(params, 'params.csv')

@@

library(hydroGOF)

KGE(flow$grid_all, flow$obs)
KGE(flow$statn_all, flow$obs)

get_kge <- function() {

}

@@

>>>>

---
title: "Fourmile Calibrations"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

@@

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)

@@

#write.csv(params, 'params.csv')

@@

@@

## Overall KGE

```{r kge overall, echo = F}

flow_kge_all <- flow %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling(full_width = F)

## Model run KGE by water year

```{r kge by year, echo = F}

flow_year <- flow %>%
  mutate(WY = calcWaterYear(date)) %>%
  group_by(WY) %>%
  summarize(grid2011 = KGE(grid_2011, obs),
            grid2012 = KGE(grid_2012, obs),
            grid2013 = KGE(grid_2013, obs),
            grid2014 = KGE(grid_2014, obs),
            grid2015 = KGE(grid_2015, obs),
            grid2016 = KGE(grid_2016, obs),
            grid2017 = KGE(grid_2017, obs),
            grid2018 = KGE(grid_2018, obs),
            grid2019 = KGE(grid_2019, obs),
            grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs),
            statn2011 = KGE(statn_2011, obs),
            statn2012 = KGE(statn_2012, obs),
            statn2013 = KGE(statn_2013, obs),
            statn2014 = KGE(statn_2014, obs),
            statn2015 = KGE(statn_2015, obs),
            statn2016 = KGE(statn_2016, obs),
            statn2017 = KGE(statn_2017, obs),
            statn2018 = KGE(statn_2018, obs),
            statn2019 = KGE(statn_2019, obs),
            statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'WY', values_from = 'kge')

flow_kge %>%
  kable(.) %>%
  kable_styling()

flow_plot <- flow_year %>%
  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
  mutate(WY = as.factor(WY))

kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
  theme_bw()

ggplotly(kge_plot_wy)

## Model run KGE plots by water year

```{r wy plots, echo = F}

plot_kge <- function(wateryear) {
  flow_plot %>%
    filter(WY == wateryear) %>%
    ggplot(aes(x = model_run,
               y = kge)) + 
    geom_col() + 
    ggtitle(wateryear) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))
}

name <- levels(flow_plot$WY)

lapply(name, plot_kge)
